\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[left=0.6in,top=0.6in,right=0.6in,bottom=0.6in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome5}

% Set paragraph spacing and indentation
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

% Page setup
\pagestyle{empty}

% Tight section formatting to match the original spacing
\titleformat{\section}{
  \normalfont\bfseries\large
}{}{0em}{}[\vspace{1pt}\titlerule]

\titlespacing{\section}{0pt}{10pt}{4pt}

% Tight lists layout with reduced left padding/margin
\setlist[itemize]{leftmargin=1.0em, nolistsep, topsep=1pt, parsep=1pt, itemsep=1pt}

\begin{document}

% Header - Large centered name in Small Caps with tight spacing
\begin{center}
    {\huge \textsc{Kolkuri Priyanka}} \\ \vspace{-2pt}
    \renewcommand{\arraystretch}{0.5}
    \begin{tabular}{c}
        \small \faPhone\ +91 9949647053 \quad \faEnvelope\ kolkuripriyanka04@gmail.com \\
        \hline
    \end{tabular}
\end{center}
\vspace{-8pt}

% Education Section
\section*{Education}
\textbf{MNR College of Pharmacy} \hfill \textbf{Dec 2021 -- Jul 2025} \\
\textit{Bachelor of Pharmacy}

\vspace{2pt}
\textbf{Narayana Junior College} \hfill \textbf{Jun 2019 -- May 2021} \\
\textit{BiPC}

\vspace{2pt}
\textbf{Karuna High School} \hfill \textbf{Jun 2009 -- May 2019} \\
\textit{State Board of Secondary Education TS}

% Work Experience Section
\section*{Work Experience}
\textbf{Dr.MACs Bio-Pharma Private Limited, Hyderabad}
\begin{itemize}
    \item Operated and monitored industrial chemical reactors under cleanroom and safety guidelines.
    \item Acquired practical experience with reaction scale-up processes and basic pharmaceutical synthesis.
    \item Assisted senior chemists in testing, optimization, and maintaining operational batch records.
\end{itemize}

% Technical Skills Section
\section*{Technical Skills}
\vspace{1pt}
\textbf{Pharmacy \& Clinical Practice:} Patient Counseling, Clinical Pharmacy, Pharmacology, Anatomy \& Physiology \\
\textbf{Quality Control \& Laboratory:} Analytical Techniques, GMP \& GLP Compliance, Lab Safety, Documentation \\
\textbf{Technical Tools:} Microsoft Office (Word, Excel, PowerPoint), Basic Data Analysis

% Additional Skills Section
\section*{Additional Skills}
\begin{itemize}
    \item Leadership \& Team Collaboration
    \item Time Management \& Task Prioritization
    \item Professional Work Ethics \& Compliance
\end{itemize}

% Academic Projects Section
\section*{Academic Projects}
\vspace{2pt}
\textbf{Identification And Minimization Of Medication Errors In Tertiary Care Hospitals}
\begin{itemize}
    \item Conducted clinical chart reviews and interacted with patients to evaluate drug administration protocols.
    \item Classified clinical errors by type (prescribing, dosing, administration) and identified root causes.
    \item Developed educational guidelines and trained hospital staff to minimize recurrence and improve patient safety.
\end{itemize}

% Achievements & Certifications Section
\section*{Achievements \& Certifications}
\begin{itemize}
    \item Certification For Participation In Quiz Competition At JNTU Sultanpur.
    \item Participated and got Certificate in various Poster and Oral Presentations.
\end{itemize}

% Personal Details Section
\section*{Personal Details}
\vspace{2pt}
\begin{tabular}{@{}ll}
    \textbf{Date of Birth:} & 04-01-2004 \\
    \textbf{Father Name:} & Kolkuri Krishna \\
    \textbf{Languages Known:} & English, Telugu, Hindi \\
    \textbf{Address:} & Kyasaram, Telangana, India \\
\end{tabular}

% Interests Section
\section*{Interests}
\begin{itemize}
    \item Pharmaceutical Research
    \item Listening to music, Dancing
\end{itemize}

\end{document}
